Coherent optical creation of a single molecule

### 2020-11-25 paper.tex
Move figures up a little
Update experimental numbers

@@

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    Inset: pulse sequence for the lifetime measurement.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as
    $P_\textrm{tweezer}^{2.58}\cdot\!2\pi\!\cdot29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
% or
% $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
This number is close to the value of
$2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance fitted to
    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
    where $P$ is the power in the tweezer,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The small $P^2$ term included in the fit is caused by the effective magnetic field
    generated by the tweezer, which is perpendicular to the real magnetic field.
    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
    $b=-3.186(9)~\mathrm{kHz/mW^2}$
    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
    The detuning is calculated using the PA frequency fitted in (a).
    The fitting results are $a=-2\pi\cdot\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
    $b=4\pi^2\cdot\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
$2\pi \times 12.1(3)~\mathrm{MHz}$.
This gives a matrix-element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}

>>>>

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{imgs/fig-lifetime.pdf}
  \caption{
    (a) Direct measurement of molecule lifetime in a trap of depth $3.75~\mathrm{mW}$.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.199(9)~\mathrm{ms}$
    measured from the Raman transition data.
    Inset: pulse sequence for the lifetime measurement.
    (b) Two-body atom lifetime of $5(1)~\mathrm{ms}$
    in a trap of depth $3.75~\mathrm{mW}$ caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as
    $P_\textrm{tweezer}^{2.58}\times\!2\pi\!\times29.3(17)~\mathrm{mHz/mW^{2.58}}$ on a log-log scale;
    this is consistent with a two-photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-lifetime}}
\end{figure}

@@

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{imgs/fig-det.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    The detuning is calculated from the closest $v'=0$ PA frequency at $288703.6~\mathrm{GHz}$.
    (a) The light shift of the Raman resonance fitted to
    $(f_{R0}+a\cdot P+b\cdot P^2)+c\cdot P/\Delta$
    where $P$ is the power in the tweezer,
    $\Delta\equiv f_{\mathrm{PA}0} - f_{\mathrm{tweer}}$ is the detuning from
    the PA resonance frequency $f_{\mathrm{PA}0}$.
    The small $P^2$ term included in the fit is caused by the effective magnetic field
    generated by the tweezer, which is perpendicular to the real magnetic field.
    The fitting results are $f_{\mathrm{PA}0}=288711~\mathrm{GHz}$,
    $f_{R0}=770.20052(2)~\mathrm{MHz}$, $a=8.78(7)~\mathrm{kHz/mW}$,
    $b=-3.186(9)~\mathrm{kHz/mW^2}$
    and $c=16.43(2)~\mathrm{MHz\cdot GHz/mW}$.
    (b) Raman Rabi frequency ($\Omega_R$) fitted to $(a + b/\Delta)\cdot P^{1.29}$.
    The detuning is calculated using the PA frequency fitted in (a).
    The fitting results are $a=-2\pi\times\!0.41(2)~\mathrm{kHz/mW^{1.29}}$
    $b=4\pi^2\times\!167(2)~\mathrm{kHz\cdot\!GHz/mW^{1.29}}$.
    (c) Tweezer power dependency of light shift (top) and Raman Rabi frequency (bottom)
    on a log-log plot showing the power-law scaling.
    \label{f-det}}
\end{figure*}

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times181.3(1)~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
This number is within $50~\mathrm{\%}$
of the value $2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory.

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.15(1)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 6.34(8)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $\Omega_a$, is
$2\pi\times 5.23(6)~\mathrm{MHz}$.
This gives a matrix-element ratio $\Omega_m/\Omega_a$ of $67.1(8)$,
which is close to the theory prediction of $77.7$~(Table~\ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $\Omega_R $ & $-$ & $2\pi \times 15.3~\mathrm{kHz}$ \\
    $\Gamma_s$ & $-$ & $ 2\pi \times 533~\mathrm{Hz}$ \\
    $\Omega_m$ & $2\pi \times 351.1(2)~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 5.23(6)~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $67.1(8)$ & $77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of $\Omega_R,\Gamma_s, \Omega_m, \Omega_a$. $\Omega_R$ and $ \Gamma_s $ are reported at $145~\mathrm{GHz}$ detuned from the $v' = 0$ state. All numbers are reported at $3.75$ mW tweezer power. }
  \label{tab:rabi_freqs}
\end{table}
